\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-13 doc/sw-system.tex
Closed #121

In this section we present our findings about the performance of the \SW system,
in terms of the information  contributed by the crowd in
\Sref{sec:results:crowd}, the speed of the system, and the overall
classifications of the training set that they made.

% PJM IS HERE.

@@

@@

We define the following properties of the crowd, as characterised by their
agents, and plot their distributions in
\Fref{fig:crowd:cornerplot}.
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified
by a volunteer. In \StageOne, the mean effort per agent was 263; in the shorter
\StageTwo it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In \StageOne, the mean experience per agent was 29;
in \StageTwo (where the training image frequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gained
per classification (in bits) by that volunteer,  $\skill$ for subjects which
have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
$\skill = 0.0$, while perfect classifiers have $\skill = 1.0$. All agents start
with $\skill = 0.0$. The skill of  an agent increases as training subjects are
classified, and the agent's estimates of its confusion matrix elements improve.
In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's
{\it test subject} classification history, a quantity representative of the
total contribution to the project made by that volunteer (see the appendix for
more discussion of this quantity). The classifications of training images
determine the skill, while the classification of test images determines
contribution.  In \StageOne, the mean  contribution per agent was
34.9 bits; in \StageTwo it was 33.5.
%
\item{\noindent\bf ``Information:''} The actual total information $\information$
generated by the agent during the volunteer's classification activity. This
quantity depends on the value of each subject's lens probability when that
subject was presented to the volunteer (simply because information gain is
defined in terms of posterior relative to prior probabilities,
\Aref{appendix:swap}).  Because of this, we expect this quantity to be noisier
than the ``contribution'' defined above.
%
\end{description}

@@

We now quantify the performance of the \SW system in terms of the recovery of
the training set images. At \StageOne, this set contains around 5712 simulated
lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
rate (TPR, the number of sims correctly detected divided by the total number of
sims in the training set), and the false positive rate (FPR, the number of duds
incorrectly detected  divided by the total number of duds in the training set), both
for a given sample of detections defined by a particular probability threshold,
which varies along the curves.  In both stages, these curves show that true
positive rates of  around 90\% were achieved, at very low false positive rates.

>>>>

In this section we present our findings about the performance of the \SW system,
in terms of the classification of the training set, the  information contributed
by the crowd, and the speed at which the image set was classified.

@@

We first quantify the performance of the \SW system in terms of the recovery of
the training set images. At \StageOne, this set contains around 5712 simulated
lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
rate (TPR, the number of sims correctly detected divided by the total number of
sims in the training set), and the false positive rate (FPR, the number of duds
incorrectly detected  divided by the total number of duds in the training set), both
for a given sample of detections defined by a particular probability threshold,
which varies along the curves.  In both stages, these curves show that true
positive rates of  around 90\% were achieved, at very low false positive rates.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

@@

To investigate the properties of the \sw crowd, as characterised by their
agents, we define the following quantities and plot their distributions in
\Fref{fig:crowd:cornerplot}.
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified
by a volunteer. In \StageOne, the mean effort per agent was 263; in the shorter
\StageTwo it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In \StageOne, the mean experience per agent was 29;
in \StageTwo (where the training image frequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gained
per classification (in bits) by that volunteer,  $\skill$ for subjects which
have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
$\skill = 0.0$, while perfect classifiers have $\skill = 1.0$. All agents start
with $\skill = 0.0$. The skill of  an agent increases as training subjects are
classified, and the agent's estimates of its confusion matrix elements improve.
In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's
{\it test subject} classification history, a quantity representative of the
total contribution to the project made by that volunteer (see the appendix for
more discussion of this quantity). The classifications of training images
determine the skill, while the classification of test images determines
contribution.  In \StageOne, the mean  contribution per agent was
34.9 bits; in \StageTwo it was 33.5.
%
\item{\noindent\bf ``Information:''} The actual total information $\information$
generated by the agent during the volunteer's classification activity. This
quantity depends on the value of each subject's lens probability when that
subject was presented to the volunteer (simply because information gain is
defined in terms of posterior relative to prior probabilities,
\Aref{appendix:swap}).  Because of this, we expect this quantity to be noisier
than the ``contribution'' defined above.
%
\end{description}

@@
